\documentclass[10pt]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{hyperref}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}

\begin{document}
\begin{center}
{\Large FRC 566.001 — Entropy–Coherence Reciprocity and UCC (Scientific Draft)}\\
{\large October 2025}\\[4pt]
H. Servat
\end{center}

\section*{1. Introduction}
We formalize the FRC 566 reciprocity between entropy $S$ and coherence $C$ and the associated flow equation (UCC). The goal is to provide unit–consistent definitions, thermodynamic projections, and reproducible validations without any extra metaphors or layer taxonomies.

\section*{2. Definitions and Units}
Entropy $S$ is measured in nats (information layers) or J/K (thermodynamic layers). Coherence $C$ is a dimensionless scalar gauge. We adopt two conventions for the coherence constant $k_*$:
\begin{itemize}
  \item information/cognition layers: $k_*=1$ (nats),
  \item thermo/physical layers: $k_*=k_B$ (Boltzmann constant).
\end{itemize}
Regularization for numerical work uses $C_\varepsilon = 1/(Z^2+\varepsilon)$ with small $\varepsilon>0$.

\section*{3. Reciprocity Law}
The core relationship is
\begin{equation}
 dS + k_*\, d\ln C = 0, \qquad \Rightarrow \qquad S + k_*\ln C = \text{const.}
\end{equation}
In information form, with a distribution $p$, define $C[p]=\exp[-H(p)/k_*]$ where $H$ is Shannon entropy (nats). Then KL divergence and mutual information yield coherence ratios and coupling penalties:
\begin{align}
\mathrm{RER}(p\!\to\!q) &= \frac{C[q]}{C[p]} = \exp\!\big[ -D_{\mathrm{KL}}(p\|q)/k_* \big],\\
I(X;Y) &= D_{\mathrm{KL}}(p_{XY}\|p_Xp_Y) \quad \Rightarrow \quad C_{XY}=\exp[-I/k_*].
\end{align}
Thermodynamic projection (isothermal) gives the unit–consistent free–energy relation
\begin{equation}
 \Delta G = -\,k_* T\, \Delta \ln C.
\end{equation}

\section*{4. Universal Coherence Condition (UCC)}
We define the local flow form
\begin{equation}
 \partial_t \ln C = -\nabla\!\cdot J_C + S_C, \qquad J_C = -D_C\,\nabla \ln C,
\end{equation}
with $D_C\!>\!0$. An energy–like dissipation follows under suitable boundary conditions (Neumann/Dirichlet):
\begin{equation}
 \sigma(t) \equiv k_* D_C \int \|\nabla \ln C\|^2\, dV \;\ge\; 0.
\end{equation}
Linear well–posedness holds for the diffusion–reaction form; nonlocal kernels (fractional Laplacian class) can be admitted if the operator remains dissipative.

\section*{5. Worked Examples (Reproducible)}
\textbf{(A) Chemical toy (isothermal).} Small dataset fit of $\Delta G$ vs $\Delta\ln C$ validates slope $-k_BT$.\\
\textbf{(B) Stochastic field (OU + coherence drift).} Add drift $\propto \nabla\ln C$; demonstrate stationary $\ln C$ profile and nonnegative $\sigma(t)$.\\
\textbf{(C) Learning system (classifier).} Coherence–regularized training: $\mathcal{L}=\mathrm{CE}+\lambda H(Z)/k_*$ where $H(Z)$ is Gaussian entropy of features; empirically fit $\Delta S\approx -k_*\Delta\ln C$ and report calibration/OOD deltas.

\section*{6. Validation}
We compute slopes and $R^2$ for $\Delta S$ vs $-k_*\Delta\ln C$ across examples; verify UCC dissipation; include KS tests against nulls for coherence concentration.

\section*{7. Limits and Identifiability}
Discuss gauge freedom in $C$, calibration of $k_*$, and sensitivity to regularization $\varepsilon$, grid, and boundary conditions.

\section*{8. Reproducibility}
Code lives under \texttt{code/566/} with a single command to regenerate all figures and pack artifacts. A GitHub Release triggers Zenodo archiving.

\end{document}

